### 2023-09-13 main.tex
oiu

\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz} 

@@

We will prove that 

@@

	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Therefore, we call $\Lambda_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We chose $z=\Lambda_{\bm{m}}+\epsilon$ 
	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)=1

@@

	(\Lambda_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\Lambda_{m}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\Lambda_{\bm{m}}+\epsilon-H)R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\left(\Lambda_{\bm{m}}+\epsilon-H\right)=\left(\Lambda_{\bm{m}}-H\right)<\infty

@@

		&\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}H\right)^{n}(\Lambda_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\Lambda_{\bm{m}}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\Lambda_{\bm{m}}+\epsilon-\Lambda_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty

@@

	\sum_{m=0}^{L}  (\Lambda_{\bm{m}}-H)\lim_{\epsilon\to 0}\epsilon R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H,\Lambda_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\Lambda_{\bm{m}}+\epsilon-H\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	WH_{0}=HW

@@

Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$, one can show that 

@@

	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|

@@

		W=&\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\
		=&\lim_{\epsilon\to 0}\sum_{m=0}^{L}\epsilon\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}^{Q}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}

@@

		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}^{Q}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}^{Q}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}^{Q}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\

@@

		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)^{-1-n}(Q_{0}^{2L})^{n}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}^{Q}+\epsilon)^{-1-n}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}\right\}^{k}
		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{B_{1}^{2L-1}\left((\Lambda_{m}^{Q}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}\right\}^{k}

@@

		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

@@

		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)

@@

		\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}

@@

	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle

@@

@@

	&SYM\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

as a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as

@@

and using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as

@@

The aim of this section is to give an answer to these questions. We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term. Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case. 

>>>>

\cite{Alcaraz:1992zc} \cite{Sklyanin:1988yz} \\
As observed in Subsection \ref{subsection-exact}, we have found two similarity transformations, namely $S_{1}$ and $S_{2}$ that map the original Hamiltonian $H$ onto a simpler one $H^{''}$, that although non-stochastic, allows to compute the explicit expression of the steady state correlations. To complete the picture, in this section we aim to find a further similarity transformation, called $W$, that maps $H^{''}$ onto $H_{0}$ that will be defined as the original Hamiltonian where the boundaries are set diagonal. Therefore, these boundaries do not produce any current and this $H_{0}$ is called \textit{equilibrium Hamiltonian}. For this reason, we say that the process is mapped onto equilibrium, indeed, using the sequence of transformations one can go from non-equilibrium to equilibrium and back.
This can be represented by the following diagram 
The eigenvectors and the eigenvalues of $H_{0}$ are known and they have been found in \cite{belliard2} and \cite{belliard2011nested} using the nested Bethe ansatz. 
As a consequence, this allows to find again the steady state of $H$, by applying the sequence of transformation to the vacuum state, i.e. a state where all the sites are empty. This transformation $W$ is non-local and requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM). 

@@

 We denote by $\bm{m}=(m_{1},\ldots,m_{N})$ an $N-$dimensional vector where each $m_{i}$ means the total occupation over the chain of each species $i\in\{1,\ldots,N\}$. Therefore, we call $\mathcal{E}_{\bm{m}}$ and $|\Psi_{\bm{m}}^{0}\rangle$ the eigenvalue and the eigenvector of $H^{0}$ that correspond to a certain $\bm{m}$. We prove that 

@@

	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

In order to be well defined $z$ must not be an eigenvalue of $H^{''}$. We chose $z=\mathcal{E}_{\bm{m}}+\epsilon$ 
	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)=1

@@

	(\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\Lambda_{m}+\epsilon)|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|=\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{m}^{0}|=\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|,

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L} (\mathcal{E}_{\bm{m}}+\epsilon-H^{''})R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)=\left(\Lambda_{\bm{m}}-H^{''}\right)<\infty

@@

		&\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\sum_{n=0}^{\infty}\left((\mathcal{E}_{\bm{m}}+\epsilon)^{-1}H^{''}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|
		\lim_{\epsilon\to 0}\epsilon\sum_{n=0}^{\infty}\left((\Lambda_{\bm{m}}+\epsilon)^{-1}\mathcal{E}_{\bm{m}}\right)^{n}(\mathcal{E}_{\bm{m}}+\epsilon)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|=\lim_{\epsilon\to 0}\epsilon\left(\mathcal{E}_{\bm{m}}+\epsilon-\mathcal{E}_{\bm{m}}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|\\=&|\Psi_{\bm{m}}^{0}\rangle\langle\Psi_{\bm{m}}^{0}|<\infty

@@

	\sum_{m=0}^{L}  (\mathcal{E}_{\bm{m}}-H^{''})\lim_{\epsilon\to 0}\epsilon R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|=0

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  \Lambda_{\bm{m}}R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\, |\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)H_{0}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|H_{0}= H^{''}\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  R(H^{''},\mathcal{E}_{\bm{m}}+\epsilon)|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	W= \lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}  \left(\mathcal{E}_{\bm{m}}+\epsilon-H^{''}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

	WH_{0}=H^{''}W

@@

Arguing as in section \ref{SectionNonLocalTrasformation} and using the resolvent operator of $Q_{2L}$ with eigenvalues $\Lambda_{m}$, one can show that 

@@

	W=\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle \langle \Psi_{m}^{0}|

@@

		W=&\lim_{\epsilon\to 0}\epsilon\sum_{m=0}^{L}\left((\Lambda_{m}+\epsilon)-Q_{0}^{2L}-2\Delta B_{1}^{2L-1}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|\\
		=&\lim_{\epsilon\to 0}\sum_{m=0}^{L}\epsilon\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|
		\lim_{\epsilon\to0}\sum_{m=0}^{L}\sum_{k=0}^{L}\Delta^{k}2^{k}\left\{\left((\lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}|\Psi_{m}^{0}\rangle\langle \Psi_{m}^{0}|

@@

	\lim_{\epsilon\to 0}\epsilon\left((\Lambda_{m}+\epsilon)I-Q_{0}^{2L}\right)^{-1}=\text{diag}\left\{0,\ldots,0,1,0,\ldots,0\right\}

@@

		&\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\left((\lambda_{m}+\epsilon)-Q_{0}^{2L}\right)^{-1}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{\sum_{n=0}^{\infty}\left((\Lambda_{m}+\epsilon)^{-1}Q_{0}^{2L}\right)^{n}(\Lambda_{m}+\epsilon)^{-1}B_{1}^{2L-1}\right\}^{k}\\

@@

		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}+\epsilon)^{-1-n}(Q_{0}^{2L})^{n}B_{1}^{2L-1}\right\}^{k}=\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{(\Lambda_{m}+\epsilon)^{-1-n}B_{1}^{2L-1}\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)^{n}\right\}^{k}
		\sum_{k=0}^{L}2^{k}\Delta^{k}\left\{B_{1}^{2L-1}\left((\Lambda_{m}+\epsilon)-\left(Q_{0}^{2L}-2(D_{2,2}^{2L}+D_{1,1}^{2L})\right)\right)^{-1}\right\}^{k}

@@

		W=&\lim_{\epsilon\to 0}\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM\left(\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

where $\Lambda_{\bm{m}}$ are the eigenvectors of $Q_{0}^{2L}$ corresponding to a configuration $\bm{m}$ of the chain. \\

@@

		W=&\lim_{\epsilon\to 0}\epsilon\sum_{\bm{m}\,:\,|\bm{m}|=L}\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}=0}^{L}\mathbbm{1}_{\{k_{1}+\cdots+k_{N-1}\leq L\}}2^{k_{1}+\ldots+k_{N-1}}\Delta_{1}^{k_{1}}\cdots\Delta_{N-1}^{k_{N-1}}\\&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)

@@

		\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle \langle \Psi_{\bm{m}}^{0}|

@@

&SYM_{k_{1},\ldots,k_{N-1}}\left(\left\{\left(\Lambda_{\bm{m}}^{Q}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\},\ldots,\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}\right)\\
=&\frac{1}{k_{1}!\cdots k_{N-1}!}\sum_{\sigma\in Sym}\left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{1})}^{2L-1}\right\}\cdots \left\{\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{\sigma(i_{k_{1}}+\ldots+i_{k_{N-1}})}^{2L-1}\right\}

@@

	\lim_{\epsilon\to 0}	\epsilon\left(\Lambda_{\bm{m}}+\epsilon-Q_{2L}^{0}\right)^{-1}|\Psi_{\bm{m}}^{0}\rangle=|\Psi_{\bm{m}}^{0}\rangle

@@

\end{equation} whose eigenvalue is $\Lambda_{0}$. 

@@

	&SYM\left(\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{1}^{2L-1}\right\}^{k_{1}},\ldots,\left\{\left(\Lambda_{0}+\epsilon-Q_{2L}^{0}\right)^{-1}B_{N-1}^{2L-1}\right\}^{k_{N-1}}\right)

@@

As a consequence we have that, for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as

@@

Moreover, using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as

@@

The aim of this section is to answer to these questions. We first define the process on a chain in order to obtain average occupation evolution equations with $N-1$ discrete Laplacians and a reaction term. Second we construct the Lie algebraic description and we use it to prove absorbing duality in this general case. 
